Belowground sink limitation alters growth and carbon balance of *Eucalyptus* seedlings

### 2016-03-08 manuscript/manuscript_pve.Rmd
now have corrected model (from BM) and it runs through plotting scripts for manuscript
regenerated daily model output script for time_course figures

renamed orginal mass model script (possibly delte)

spelling edits to manuscript

\
(1)
$$P_i = L\left(\frac{C_\mathrm{day'i}~\sigma_\mathrm{s}}{\epsilon_\mathrm{c}}\right) - R$$
where *L* is total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C g mass^-1^ d^-1^,, explained below), $\sigma$~s~ is a self-shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^). Total respiration was calculated as

@@

##Modelling seedling biomass
The default model (*M*~free~), successfully optimized a LMF (21.6 %) which then allowed the model to predict mean harvest total biomass of free seedlings within 1.2 %. Using this optimized LMF, the total biomass of modeled seedlings for each soil volume treatment (*M*~pots~) were on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf *C* gain (Figure `r massmodelfig`a). As a result, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the soil volume treatments when non-photosynthetic parameters were kept constant (Figure `r massmodelfig`b). As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.

@@

# Acknowledgements
We thank Burhan Amiji for for his outstanding technical assitance. We would like to thank the many Hawkesbury Institute for the Environment staff and students who provded field work help during the experimental harvest.

>>>>

\
(1)
$$P_i = L\left(\frac{C_\mathrm{day'i}~\sigma_\mathrm{s}}{\epsilon_\mathrm{c}}\right) - R$$
where *L* is total plant leaf area (m^2^), *C*~day,i~ is the predicted daily carbon assimilation (g C m^-2^ d^-1^, explained below), $\sigma$~s~ is a self-shading parameter (explained below), $\epsilon$~c~ is a biomass conversion efficiency parameter (g C g mass^-1^) and *R* is the mass based total respiration of all tissue components (g C d^-1^). Total respiration was calculated as

@@

##Modelling seedling biomass
The default model (*M*~free~), successfully optimized a LMF (22.8 %) which then allowed the model to predict mean harvest total biomass of free seedlings within 1.2 %. Using this optimized LMF, the total biomass of modeled seedlings for each soil volume treatment (*M*~pots~) were on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf *C* gain (Figure `r massmodelfig`a). As a result, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the soil volume treatments when non-photosynthetic parameters were kept constant (Figure `r massmodelfig`b). As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.

@@

# Acknowledgements
We thank Burhan Amiji for his outstanding technical assistance. We would like to thank the many Hawkesbury Institute for the Environment staff and students who helped during the experimental harvest.
